Graph Topological Aspects of Granger Causal Network Learning

### 2019-07-17 paper/paper.tex
I can have a supplementary document with proofs and extra figures.

In our finite sample implementation (see Algorithm
\ref{alg:finite_pwgc}) we add edges to $\widehat{\gcg}$ in order of
the decreasing magnitude of $F_{ij}$ instead of proceeding backwards
through $P_{k - r}$ in Algorithm \ref{alg:pwgr}.  This makes greater
use of the information provided by the test statistic $F_{ij}$,
moreover, if $x_i \gc x_j$ and $x_j \gc x_k$, it is expected that
$F_{kj} > F_{ji}$, thereby providing the same effect as proceeding
backwards through $P_{k - r}$.
\subsection{Model Order Selection}
\label{sec:model_order_selection}
There are a variety of methods to choose the filter order $p$ (see
e.g. \cite{lutkepohl2005new}), but we will focus in particular on the
Bayesian Information Criteria (BIC).  The BIC is substantially more
conservative than the popular alternative Akaiake Information Criteria
(the BIC is also asymptotically consistent), and since we are
searching for \textit{sparse graphs}, we therefore prefer the BIC,
where we seek to \textit{minimize} over $p$:

>>>>

In our finite sample implementation (see Algorithm
\ref{alg:finite_pwgc}) we add edges to $\widehat{\gcg}$ in order of
the decreasing magnitude of $F_{ij}$ instead of proceeding backwards
through $P_{k - r}$ in Algorithm \ref{alg:pwgr}.  This makes greater
use of the information provided by the test statistic $F_{ij}$,
moreover, if $x_i \gc x_j$ and $x_j \gc x_k$, it is expected that
$F_{kj} > F_{ki}$, thereby providing the same effect as proceeding
backwards through $P_{k - r}$.
\subsection{Model Order Selection}
\label{sec:model_order_selection}
There are a variety of methods to choose the filter order $p$ (see
e.g. \cite{lutkepohl2005new}), but we will focus in particular on the
Bayesian Information Criteria (BIC).  The BIC is substantially more
conservative than the popular alternative Akaiake Information Criteria
(the BIC is also asymptotically consistent), and since we are
searching for \textit{sparse graphs}, we therefore prefer the BIC,
where we seek to \textit{minimize} over $p$:
